\TheTitle

### 2015-08-16 linvis.tex
Design: Modules
Talking about the modules tab of the viewer.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/tree_view.png}
	\caption{Commit Tree View}
	\label{fig:files}
\end{figure}

The third tab shows the tree view. The tree view is what makes this tool unique
to the other tools. It provides a full view of the entire merge tree. It
originally centres at the current commit or merge, but allows a user to inspect
the other commits and merges surrounding it. A user may then navigate to any of
the commits by simply double-clicking on it.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/tree_zoom.png}
	\caption{Tree zoomed out}
	\label{fig:files}
\end{figure}

Some of the merge trees are very large, containing thousands of commits and
merges. Clicking on subtrees will cause them to minimize, only showing parts of
the tree that are of interest to the user. Furthermore, the user can zoom the
tree by scrolling the mouse wheel to see more of the topology of the tree, or
to see the details of a given part of the tree.

>>>>

\begin{figure}[h]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/modules.png}
	\caption{Commit Modules}
	\label{fig:modules}
\end{figure}

The modules tab shows the modules that are contained within the commit. Modules
are not natively recognized by git, and are not going to be present in all
repositories. In the Linux repository, authors put the module they are working
on in the one-line preview of the log-message.  We heuristically extract the
module by taking all text in the log preview until the first colon. Modules are
logical partitions of the information in the kernel. Depending on where the
author was working, modules can be general, such as ``bluetooth'' and
``wireless'', or can be quite specific for individual hardware, such as
``ath9k\_hw'' and ``wl1251''. Like files, we are able to show what modules are
edited in merges and in commits. The image in figure \ref{fig:modules} shows
the modules for a commit. A commit will only ever have one module that it is
associated with.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/tree_view.png}
	\caption{Commit Tree View}
	\label{fig:tree}
\end{figure}

The third tab shows the tree view (\ref{fig:tree}). The tree view is what makes
this tool unique to the other tools. It provides a full view of the entire
merge tree. It originally centres at the current commit or merge, but allows a
user to inspect the other commits and merges surrounding it. A user may then
navigate to any of the commits by simply double-clicking on it.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/tree_zoom.png}
	\caption{Tree zoomed out}
	\label{fig:zoomed_tree}
\end{figure}

Some of the merge trees are very large (\ref{fig:zoomed_tree}), containing
thousands of commits and merges. Clicking on subtrees will cause them to
minimize, only showing parts of the tree that are of interest to the user.
Furthermore, the user can zoom the tree by scrolling the mouse wheel to see
more of the topology of the tree, or to see the details of a given part of the
tree.
